Determinism, Complexity, and Predictability in Computer Performance

### 2014-07-25 methods.tex
synching up

The wide range of behaviors in Figure~\ref{fig:svd-ts-colored}
provides a unique advantage, for the purposes of this paper, in that a
number of different generating processes---with a wide range of
complexities---are at work in different phases of a single time
series.  The complexity of \col and \gcc in Figures~\ref{fig:col-ipc}
and \ref{fig:gcc-ts} appears to be far more consistent over
time---probably the result of a single generating process.  \svd, in
contrast, has multiple regimes, each the result of a different
generating process.  To take advantage of this, we split the signal
into six different segments, thereby obtaining an array of examples
for the analyses in the following sections.  For notational
convenience, we refer to these 90 time-series data sets\footnote{15
  runs, each with six regimes} as {\tt dgesdd$_i$}, with $i \in
\{1\dots6\}$ where $i$ corresponds to one of the six segments of the
signal, ordered from left to right.  These segments, which were
determined visually, are shown in different colors in
Figure~\ref{fig:svd-ts-colored}.  Visual decomposition is subjective,
of course, particularly since the regimes exhibit some fractal
structure.  Thus, it may be the case that more than one generating
process is at work in each of our segments.  This is a factor in the
discussion of Section~\ref{sec:results}.

>>>>

The wide range of behaviors in Figure~\ref{fig:svd-ts-colored}
provides a unique advantage, for the purposes of this paper, in that a
number of different generating processes---with a wide range of
complexities---are at work in different phases of a single time
series.  The \col and \gcc traces in Figures~\ref{fig:col-ipc} and
\ref{fig:gcc-ts} appear to be far more consistent over time---probably
the result of a single generating process with consistent complexity.
\svd, in contrast, has multiple regimes, each the result of a
different generating process.  To take advantage of this, we split the
signal into six different segments, thereby obtaining an array of
examples for the analyses in the following sections.  For notational
convenience, we refer to these 90 time-series data sets\footnote{15
  runs, each with six regimes} as {\tt dgesdd$_i$}, with $i \in
\{1\dots6\}$ where $i$ corresponds to one of the six segments of the
signal, ordered from left to right.  These segments, which were
determined visually, are shown in different colors in
Figure~\ref{fig:svd-ts-colored}.  Visual decomposition is subjective,
of course, particularly since the regimes exhibit some fractal
structure.  Thus, it may be the case that more than one generating
process is at work in each of our segments.  This is a factor in the
discussion of Section~\ref{sec:results}.

### 2014-07-25 model.tex
synching up

@@

@@

  \caption{Predicted ($p_j$) versus true values ($c_j$) for forecasts of \col,
     \gcc, and \svdfive and all four prediction strategies.
  }

@@

MASE scores for all 360 experiments are tabulated in the three
middle columns in Table~\ref{tab:error}.
\begin{table*}
\caption{Mean
absolute scaled error (MASE) scores and weighted permutation entropies for all eight
   processes studied in this paper}
  \begin{center}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill} } cccccc}
  \hline\hline Signal & LMA MASE & \arima MASE & na\"{i}ve MASE & RW MASE & WPE \\
  \hline

>>>>

These four forecast methods were chosen to be a representative
sampling of standard prediction strategies, but they do not, of
course, cover that space exhaustively.  Our goal here is an empirical
assessment of the relationship between predictability and complexity,
not formal results about a ``best'' predictor for a given time series.
From a practitioner's standpoint, it would be useful to know \emph{ a
  priori} if a time series contains enough predictive structure to
make it worth spending the time and effort searching for a good
forecast method.  It would also be useful to know if a given method is
inadequate---that is, if an alternative method could do better and so
one should continue searching.  \alert{[[need to check that this is not
    redundant, given the other text in this section (and elsewhere in
    the paper).  it may be better to put this in the conclusion.]]}

@@

\alert{We need to go through this section and the results section,
  rewriting as necessary to account for our addition of RW to the
  table}

@@

  \caption{Predicted ($p_j$) versus true values ($c_j$) for forecasts
    of \col, \gcc, and \svdfive made using each of the four 
    strategies studied here.  }

@@

MASE scores for all 360 experiments are tabulated in the three
middle columns in Table~\ref{tab:error}.
\begin{table*}
\caption{Mean absolute scaled error (MASE) scores and weighted
  permutation entropies for all eight processes studied in this paper.
  LMA $=$ Lorenz method of analogues; RW $=$ random-walk prediction.}
  \begin{center}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill} } cccccc}
  \hline\hline Signal & LMA MASE & \arima MASE & na\"{i}ve MASE & RW MASE & WPE \\
  \hline
